---
title: "Ismet Tez"
author: "Ismet Ozer"
date: "26 07 2021"
runtime: shiny
output:
  html_document: 
    code_folding: hide
    toc: true
    toc_float: true
  pdf_document: 
    latex_engine: xelatex
    toc: true
    toc_depth: 5
---

```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, comment = NA)
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```


```{r message=FALSE, warning=FALSE}

library(flextable)
library(report)
library(reactable)
library(skimr)
library(dlookr)
library(performance)
library(see)
library(car)
library(dplyr)
library(tidyr)
library(pastecs)
library(broom)
library(ggplot2)
library(ggfortify)
library(plotly)
library(ggpubr)
library(GGally)
library(performance)
library(modelbased)
library(DataExplorer)
```

# Loading and handling data

```{r}
tez <- read.csv("../data/finalData.csv", sep = ";")

tez <- tez %>% dplyr::rename(IGT = NET,
                             IGT_1 = NET1,
                             IGT_2 = NET2,
                             IGT_3 = NET3,
                             IGT_4 = NET4,
                             IGT_5 = NET5,
                             BART = adjustedaveragepumpcount,
                             BART_1 = adjustedaveragepumpcount_10,
                             BART_2 = adjustedaveragepumpcount_20,
                             BART_3 = adjustedaveragepumpcount_30)

# Barratt Impulsiveness Scale
## Barratt reversing items
bar_rev_cols <- c("barratt_1", "barratt_5","barratt_6","barratt_11","barratt_15")

tez[, bar_rev_cols] <- 5 - tez[, bar_rev_cols]

tez[, bar_rev_cols] <- lapply(tez[, bar_rev_cols], as.integer)

## Total and subscales of Barratt scores
tez <- tez %>% mutate(barratt_total = rowSums(select(., c(barratt_1:barratt_15))),
                      barratt_atten = rowSums(select(., c(barratt_1, barratt_5, barratt_6, barratt_11, barratt_15))),
                      barratt_motor = rowSums(select(., c(barratt_4, barratt_10, barratt_12, barratt_13, barratt_14))),
                      barratt_atten = rowSums(select(., c(barratt_2, barratt_3, barratt_7, barratt_8, barratt_9))))

# Sensation Seeking Scale
## Total SSS
tez <- tez %>% mutate(sss_total = rowSums(select(., c(sss_1:sss_8))))

# Ok-Religious Attitudes
## Ok-Religious Attitudes reversing items
ok_rev_cols <- c("ok_religious_attitudes_1", "ok_religious_attitudes_2")

tez[, ok_rev_cols] <- 6 - tez[, ok_rev_cols]

tez[, ok_rev_cols] <- lapply(tez[, ok_rev_cols], as.integer)

## Total and subscales of Ok-Religious Attitudes Scale
tez <- tez %>% mutate(okRelig_total = rowSums(select(., c(ok_religious_attitudes_1:ok_religious_attitudes_8))),
                      okRelig_cog = rowSums(select(., c(ok_religious_attitudes_1,ok_religious_attitudes_2))),
                      okRelig_feel = rowSums(select(., c(ok_religious_attitudes_3,ok_religious_attitudes_4))),
                      okRelig_behav = rowSums(select(., c(ok_religious_attitudes_5,ok_religious_attitudes_6))),
                      okRelig_rel2god = rowSums(select(., c(ok_religious_attitudes_7,ok_religious_attitudes_8))))

# Intuitive Religion Scale
## reversing items
int_rev_cols <- c("intuitive_religion_3", "intuitive_religion_4", "intuitive_religion_5")

tez[, int_rev_cols] <- 6 - tez[, int_rev_cols]

tez[, int_rev_cols] <- lapply(tez[, int_rev_cols], as.integer)

## Total Intuitive Religion Scale score
tez <- tez %>% mutate(intuRelig_total = rowSums(select(., c(intuitive_religion_1:intuitive_religion_5))))

#Removing variables
tez <- tez %>% select(-barratt_1:-barratt_15,
                      -sss_1:-sss_8,
                      -religion,
                      -ok_religious_attitudes_1: -ok_religious_attitudes_8,
                      -intuitive_religion_1:-intuitive_religion_5)

tez$education <- ifelse(tez$bau_student == 1, 2, tez$education)

# Correcting data types
tez$bau_student <- factor(tez$bau_student, labels = c("Student", "Not Student"))
tez$group <- factor(tez$group, labels = c("Punishing", "Rewarding", "Control"))
tez$sex <- factor(tez$sex, labels = c("Female", "Male"))
tez$education <- factor(tez$education, labels = c("Graduate", "Undergraduate", "Associate", "Highschool"))
tez$dominant_hand <- factor(tez$dominant_hand, labels = c("Left", "Right"))
tez$place <- factor(tez$place, levels = c(1:5), labels = c("Metropolis", "City",	"Town", "Borough", "Village"))
tez$income <- factor(tez$income, levels = c(1:5), labels = c("Very well", "Good", "Not bad", "Bad", "Very bad"))
tez$IGT_awareness_2 <- factor(tez$IGT_awareness_2, labels = c("Yes", "No"))
tez$IGT_awareness_3_A <- factor(tez$IGT_awareness_3_A, labels = c("Win", "Lose"))
tez$IGT_awareness_4_B <- factor(tez$IGT_awareness_4_B, labels = c("Win", "Lose"))
tez$IGT_awareness_5_C <- factor(tez$IGT_awareness_5_C, labels = c("Win", "Lose"))
tez$IGT_awareness_6_D <- factor(tez$IGT_awareness_6_D, labels = c("Win", "Lose"))
tez$IGT_awareness_7 <- factor(tez$IGT_awareness_7, labels = c("1. Deck", "2. Deck", "3. Deck", "4. Deck"))

tez$barratt_code <- if (tez$barratt_total <= mean(tez$barratt_total)- sd(tez$barratt_total)) {
  tez$barratt_code = 1
} else if (tez$barratt_total >= mean(tez$barratt_total) + sd(tez$barratt_total)) {
  tez$barratt_code = 3
} else {
  tez$barratt_code = 2
}

# Group coding for barratt_total
## 1 for values < mean - sd, 2 for mean - sd < values < mean + sd, 3 for values > mean + sd
tez$barratt_code <- ifelse(
  (tez$barratt_total <= mean(tez$barratt_total) - sd(tez$barratt_total)), 1,
  ifelse(
    (tez$barratt_total >= mean(tez$barratt_total) + sd(tez$barratt_total)), 3, 2
    )
  )

tez$barratt_code <- factor(tez$barratt_code, 
                           levels = c(1:3),
                           labels = c("Low", "Medium", "High"),
                           ordered = T)

# Group coding for sss_total
## 1 for values < mean - sd, 2 for mean - sd < values < mean + sd, 3 for values > mean + sd
tez$sss_code <- ifelse(
  (tez$sss_total <= mean(tez$sss_total) - sd(tez$sss_total)), 1,
  ifelse(
    (tez$sss_total >= mean(tez$sss_total) + sd(tez$sss_total)), 3, 2
    )
  )

tez$sss_code <- factor(tez$sss_code, 
                           levels = c(1:3),
                           labels = c("Low", "Medium", "High"),
                           ordered = T)

# Group coding for okRelig_total
## 1 for values < mean - sd, 2 for mean - sd < values < mean + sd, 3 for values > mean + sd
tez$okRelig_code <- ifelse(
  (tez$okRelig_total <= mean(tez$okRelig_total) - sd(tez$okRelig_total)), 1,
  ifelse(
    (tez$okRelig_total >= mean(tez$okRelig_total) + sd(tez$okRelig_total)), 3, 2
    )
  )

tez$okRelig_code <- factor(tez$okRelig_code, 
                           levels = c(1:3),
                           labels = c("Low", "Medium", "High"),
                           ordered = T)


# Group coding for intuRelig_total
## Replacing NA values with group means

tez <- tez %>% 
  dplyr::group_by(group) %>% 
  mutate_at(vars(intuRelig_total),  funs(replace(., which(is.na(.)),
                                round(mean(., na.rm=TRUE)))))  

## 1 for values < mean - sd, 2 for mean - sd < values < mean + sd, 3 for values > mean + sd
tez$intuRelig_code <- ifelse(
  (tez$intuRelig_total <= mean(tez$intuRelig_total) - sd(tez$intuRelig_total)), 1,
  ifelse(
    (tez$intuRelig_total >= mean(tez$intuRelig_total) + sd(tez$intuRelig_total)), 3, 2
    )
  )

tez$intuRelig_code <- factor(tez$intuRelig_code, 
                             levels = c(1:3),
                             labels = c("Low", "Medium", "High"),
                             ordered = T)


# Group coding for BART awareness 
## 1 for values < 16, 2 for 15 < values < 31, 3 for values > 30
tez$BART_awareness_code <- ifelse(
  (tez$BART_awareness_1 <= 16), 1,
  ifelse(
    (tez$BART_awareness_1 >= 16 & tez$BART_awareness_1 <= 31), 2, 3
    )
)

tez$BART_awareness_code <- factor(tez$BART_awareness_1, 
                             levels = c(1:3),
                             labels = c("0-15", "15-30", ">30"),
                             ordered = T)



# Inserting ID numbers

tez <- tez %>% ungroup() %>% dplyr::mutate(id = row_number())
tez <- tez %>% dplyr::relocate(id, .before = bau_student)

# Removing unrelated columns

tez <- tez %>%
  select(-totalearnings:-adjustedtotalpumpcount_30,
         -currenttotal:-countDisAdvantage_total,
         -countAdvantage1,-countAdvantage2, -countAdvantage3,
         -countAdvantage4,-countAdvantage5,-countDisAdvantage1,
         -countDisAdvantage2, -countDisAdvantage3,
         -countDisAdvantage4, -countDisAdvantage5, -countDisAdvantage_total, -BART_awareness_code, 
         -IGT_awareness_1:-IGT_awareness_7,
         -deckOrderGroup, -email
         )

# Renaming columns

tez <- tez %>% dplyr::rename(
  subjective_religiosity_rating = religion_rating,
  condifence_in_gods_existance = god_exists_rating,
  impulsivity = barratt_total,
  attentional_impulsivity = barratt_atten,
  motor_impulsivity = barratt_motor,
  sensation_seeking = sss_total,
  religiosity = okRelig_total,
  cognitive_religiosity = okRelig_cog,
  emotional_religiosity = okRelig_feel,
  behavioral_religiosity = okRelig_behav,
  relation_to_god_religiosity = okRelig_rel2god,
  intuitive_religiosity = intuRelig_total
)


tez <- tez %>% dplyr::select(-contains("BART"))

```


# Data Exploration

Variables that end with "_code" are arbitrarily coded as: 

* Low is smaller than mean - sd
* High is bigger than mean + sd
* Medium is between low and high

## Introducing Data {.tabset .tabset-fade}

### All Data {.tabset .tabset-fade}

#### Factor Variables

```{r skim_factor_all}
tez %>% ungroup() %>%  
  skim() %>% yank("factor") %>% 
  flextable() %>% colformat_double(digits = 2)
```

#### Numeric Variables

```{r skim_numeric_all}
tez %>% ungroup() %>% 
  skim() %>% yank("numeric") %>% 
  flextable() %>% colformat_double(digits = 2)
```

### By Groups {.tabset .tabset-fade}

#### Factor Variables

```{r skim_factor_grouped}
tez %>% 
  skim() %>% yank("factor") %>% 
  flextable() %>% colformat_double(digits = 2)
```

#### Numeric Variables

```{r skim_numeric_grouped}
tez %>% 
  skim() %>% yank("numeric") %>% 
  flextable() %>% colformat_double(digits = 2)
```


## Distribution of participants in variables {.tabset .tabset-fade}

### All

```{r plot_bar_1half}
DataExplorer::plot_bar(select(tez, 
                              bau_student, group, sex,
                              education, dominant_hand, place)) 
```

```{r plot_bar_2half}
DataExplorer::plot_bar(dplyr::select(tez, 
                                     income, barratt_code, sss_code,
                                     okRelig_code, intuRelig_code)) 
```

### By Groups

```{r plot_bar_by_group_1half}
DataExplorer::plot_bar(select(tez,
                              -barratt_code, -sss_code,
                              -okRelig_code, -intuRelig_code),
                       by = "group", by_position = "dodge") 
```

```{r plot_bar_by_group_2half}
DataExplorer::plot_bar(select(tez, -bau_student, -sex, -education,
                               -dominant_hand, -place, - income),
                       by = "group", by_position = "dodge") 
```

## Analysis of Numeric Variables

```{r table_numeric}
tez %>% dplyr::select(-id, -id_in_group) %>% ungroup() %>% 
  diagnose_numeric() %>% 
  flextable() %>% colformat_double(digits = 2) %>% 
  footnote(i = 1, j = 8:9, inline = T, part = "header",
           value = as_paragraph(c("Number of values that are 0",
                                  "Number of negative values")))
```

$~$

## Analysis for Outliers

```{r table_outliers}
tez %>% ungroup() %>% dplyr::select(-id, -id_in_group) %>%
  diagnose_outlier() %>% 
  flextable() %>% colformat_double(digits = 2) %>% 
  footnote(i = 1, j = c(2, 5:6), inline = T, part = "header",
           value = as_paragraph(c("Outlier count",
                                  "Mean when outliers included", 
                                  "Mean when outliers excluded")))
```

$~$

## Outcome Variable Statistics by Groups {.tabset .tabset-fade}

### IGT

```{r igt_stat.desc}
by(tez$IGT, tez$group, 
   stat.desc, basic = F, norm = T)
```

$~$

### BART

```{r bart_stat.desc}
by(tez$BART, tez$group, 
   stat.desc, basic = F, norm = T)
```

__Interesting Points:__ 

* Punishing primes group is a little over 1 in its kurtosis statistic (kurt.2SE = 1.08). _What to do about it?_

$~$

## Plots {.tabset .tabset-fade}

### IGT {.tabset .tabset-fade}

#### Line Plot

```{r}
tez %>% tidyr::pivot_longer(cols = contains("IGT"),
                            names_to = "igt_blocks",
                            values_to = "score") %>% 
  ggplot(aes(igt_blocks, score, group = group, color = group)) + 
  stat_summary(fun.y = mean, geom = "point") + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(aes(label = round(..y.., 2)),
                   fun.y = mean, geom = "text", vjust = -.5) +
  geom_hline(aes(yintercept = 0), color = "red", liIGType = "dotted") + 
  theme_minimal() +
  labs(x = NULL,
       y = "Advantageous - Disadvantageous",
       caption = "Numbers represent means")
```

$~$

#### Bar Plot 

```{r}
tez %>% pivot_longer(col = contains("IGT"),
                     names_to = "igt_blocks",
                     values_to = "score") %>% 
  ggplot(aes(igt_blocks, score, fill = group)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = "dodge") + 
  theme_minimal() +
  labs(x = NULL,
       y = "Advantageous - Disadvantageous",
       caption = "Errorbars represent standard error of the mean")
```

### BART {.tabset .tabset-fade}

#### Line Plot

```{r}
tez %>% dplyr::select(-BART_awareness_1) %>% 
  pivot_longer(cols = contains("BART"),
               names_to = "bart_blocks",
               values_to = "score") %>% 
  ggplot(aes(bart_blocks, score, group = group, color = group)) +
  stat_summary(fun.y = mean, geom = "point") + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(aes(label = round(..y.., 2)),
               fun.y = mean, geom = "text", vjust = -.5) + 
  theme_minimal() + 
  labs(x = NULL,
       y = "Mean pumps for unexploded trials")
```

$~$

#### Bar Plot

```{r}
tez %>% dplyr::select(-BART_awareness_1) %>% 
  pivot_longer(cols = contains("BART"), 
               names_to = "bart_blocks",
               values_to = "score") %>% 
  ggplot(aes(bart_blocks, score, fill = group)) + 
  stat_summary(fun = mean, geom = "bar", position = "dodge") + 
  stat_summary(fun.data = mean_se, geom = "errorbar", position = "dodge") + 
  theme_minimal() + 
  labs(x = NULL,
       y = "Mean pumps for unexploded trials",
       caption = "Errorbars represent standard error of the mean")
```

$~$

## Correlations {.tabset .tabset-fade}

### Correlation Plot 

```{r}
tez %>% select(-id, -id_in_group) %>% 
  GGally::ggcorr(label = T, label_size = 3) 
```

$~$

### Correlation Matrix

```{r message=FALSE, warning=FALSE, }

tez %>% select(okRelig_total, intuRelig_total,
               barratt_total, sss_total,
               BART, IGT) %>% 
  GGally::ggpairs(mapping = ggplot2::aes(color = tez$group),
                  lower = list(continuous = wrap("smooth", size = .9,
                                                 position = "jitter", 
                                                 se = F, 
                                                 method = "lm")),
                  diag = list(continuous = wrap("densityDiag", 
                                                alpha = .3))) +
  theme_minimal()
  
```

$~$

### Interactive Correlation Tables {.tabset .tabset-fade}

You can sort the table in ascending or descending order by clicking on the column names.

#### All

```{r}
tez %>% ungroup() %>% dplyr::select(-id, -id_in_group) %>% 
correlate() %>% 
  reactable::reactable(compact = T, highlight = T,
    defaultColDef = colDef(format =
                             colFormat(separators = T, digits = 3)
                          )
                      )
```

$~$

#### By Groups

```{r}
tez %>% dplyr::select(-id, -id_in_group) %>% 
correlate() %>% 
  reactable::reactable(compact = T, highlight = T,
    defaultColDef = colDef(format =
                             colFormat(separators = T, digits = 3)
                          )
                      )
```

$~$

# ANCOVA Model

$~$

## Assumptions 

### 1. Indipendence of Covariates from the IV {.tabset .tabset-fade}

> ANCOVA assumes that the covarite is not related to the independent variable. 

We can check this assumption by creating an ANOVA model with the covariate as the DV and the religious priming groups as the IV in our study.

#### Impulsiveness

```{r}
summary(aov(barratt_total ~ group, data = tez))

report(aov(barratt_total ~ group, data = tez))
```

We can assume that the covariate of impulsiveness is not influenced by our manipulations, therefore independent of the IV.

$~$

#### Sensation-seeking

```{r}
summary(aov(sss_total ~ group, data = tez)) 

report(aov(sss_total ~ group, data = tez))
```

We can assume that the covariate of sensation-seeking is not influenced by our manipulations, therefore independent of the IV.

$~$

### 2. Homogeniety of Regression Slopes {.tabset .tabset-fade}

> ANCOVA assumes that the slopes of the regression lines, formed by the covariate and the outcome variable, should be the same for each group. 

We can check this assumption by looking for non-significant interaction between the covariate and the IV groups.

#### IGT

```{r}
car::Anova(aov(IGT ~ group:barratt_total:sss_total, data = tez))
report(aov(IGT ~ group:barratt_total:sss_total, data = tez))
```

Since there were no significant interactions between the IV and the covarite, we can assume homogeneity of regression slopes.

$~$

#### BART

```{r}
car::Anova(aov(BART ~ group:barratt_total:sss_total, data = tez))
report(aov(BART ~ group:barratt_total:sss_total, data = tez))
```

Since there were no significant interactions between the IV and the covarite, we can assume homogeneity of regression slopes.

$~$

### 3. Homogeneity of Variances (Heteroscasdicity) {.tabset .tabset-fade}

> ANCOVA assumes that residual variances for the outcome variable are homogeneous for all groups. 

We can check for this assumption applying Levene's test. 

$~$

#### IGT

```{r message=FALSE, warning=FALSE}
igt_anova <- aov(IGT ~ group, data =tez)

car::leveneTest(IGT ~ group, data = tez, center = median)

check_homogeneity(igt_anova, method = "levene")
```


Since the Levene's test suggests that residual variance distributions do not differ between groups (p > .05), we can assume homoscasdicity. 

$~$

#### BART

```{r message=FALSE, warning=FALSE}
bart_anova <- aov(BART ~ group, data = tez)

car::leveneTest(BART ~ group, data = tez, center = median)

check_homogeneity(bart_anova, method = "levene")
```

Since the Levene's test suggests that residual variance distributions do not differ between groups (p > .05), we can assume homoscasdicity. 

$~$

### 4. Normality of Residuals {.tabset .tabset-fade}

> ANCOVA assumes that the outcome variable is normally distributed. 

We can check this with Shapiro-Wilk test of normality and visualize distribution plots.

$~$

#### IGT

Shapiro-Wilk normality tests of the IGT results for groups:

```{r}
by(tez$IGT, tez$group, shapiro.test)
```

$~$

Shapiro-Wilk normality test for the IGT ANCOVA model:

```{r message=FALSE, warning=FALSE}
igt_full_ancova <- aov(IGT ~ barratt_total + sss_total + group, data = tez)

plot(check_normality(igt_full_ancova))
```

$~$

#### BART

Shapiro-Wilk normality tests of the BART results for groups:

```{r}
by(tez$BART, tez$group, shapiro.test)
```

Shapiro-Wilk normality test for the BART ANCOVA model:

```{r message=FALSE, warning=FALSE}
bart_ancova_full <- aov(BART ~ BART + sss_total + group, data = tez)

plot(check_normality(bart_ancova_full))
```

Since the Shapiro-Wilk test result was significant (p = 0.030), *we cannot assume normality* for the BART model. This non-normality seems to be influenced from the punishing prime group distributions particularly.

$~$

### 5. Linearity {.tabset .tabset-fade}

> ANCOVA assumes linearity between the covariate and the outcome variable at each level of the grouping variable. 

This can be checked by creating a grouped scatter plot of the covariate and the outcome variable.

#### IGT {.tabset .tabset-fade}

##### Impulsivity and IGT

```{r}
ggscatter(tez,
          x = "barratt_total", y = "IGT",
          color = "group", add = "reg.line") + 
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"), color = group)
  )
```

##### Sensation-seeking and IGT

```{r}
ggscatter(tez,
          x = "sss_total", y = "IGT",
          color = "group", add = "reg.line") +
  stat_regline_equation(
    aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~~"), color = group)
  )
```

$~$

#### BART {.tabset .tabset-fade}

##### Impulsivity and BART

```{r}
ggscatter(tez, 
          x = "barratt_total", y = "BART",
          color = "group", add = "reg.line") +
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"), color = group)
  )
```

##### Sensation-seeking and BART

```{r}
ggscatter(tez,
          x = "sss_total", y = "BART",
          color = "group", add = "reg.line") +
  stat_regline_equation(
    aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~~"), color = group)
  )
```

$~$

### Outliers {.tabset .tabset-fade}

> ANCOVA assumes no significant outliers in the groups.

We can check for outliers using the IQR method.

$~$

#### IGT

```{r}
tez %>% dplyr::group_by(group) %>% dplyr::select(contains("IGT")) %>% diagnose_outlier() %>%  
  flextable() %>% colformat_double(digits = 2)%>% 
  footnote(i = 1:12, j = 1, inline = T,
           value = as_paragraph(c("Punishing","Non-punishing","Control")))
```

```{r}
# Shiny

by(tez$IGT, tez$group, check_outliers, method = "iqr")

tez %>% ggplot(aes(group, IGT)) + geom_boxplot() + theme_minimal() + labs(x = NULL)
```

#### BART

```{r}
tez %>% dplyr::group_by(group) %>% dplyr::select(contains("BART"), -BART_awareness_1) %>% diagnose_outlier() %>%  
  flextable() %>% colformat_double(digits = 2) %>% 
  footnote(i = 1:12, j = 1, inline = T,
           value = as_paragraph(c("Punishing","Non-punishing","Control")))
```

```{r}
by(tez$BART, tez$group, check_outliers, method = "iqr")

tez %>% ggplot(aes(group, BART)) + geom_boxplot() + theme_minimal() + labs(x = NULL)
```

ANCOVA is quite sensitive to outliers. We need to deal with these values somehow.

$~$

### Model Assumption Visualizations {.tabset .tabset-fade}

$~$

These are the assumptions for the full ANCOVA (controlling for impulsivity and sensation-seeking) models.

$~$

#### IGT {.tabset .tabset-fade}

##### Plot 1

```{r}
check_model(aov(IGT ~ barratt_total + sss_total + group, data = tez))
```

$~$

##### Plot 2

```{r}
autoplot(igt_full_ancova, which = 1:6, nrow = 3, ncol = 2) + theme_minimal()
```

$~$

##### Metrics

```{r}
igt_full_ancova %>% augment(data = tez) %>% 
  dplyr::select(id, IGT, barratt_total, sss_total, 
                .fitted:.std.resid) %>% 
  reactable(compact = T, highlight = T, striped = T,
            columns = list(id = colDef(format = colFormat(digits = 0)),
                           IGT = colDef(format = colFormat(digits = 0)),
                           barratt_total = colDef(format = colFormat(digits = 0)),
                           sss_total = colDef(format = colFormat(digits = 0))), 
            defaultColDef = colDef(
              format = colFormat(separators = T, digits = 3)))
```

$~$

#### BART {.tabset .tabset-fade}

$~$

These are the assumptions for the full ANCOVA (controlling for impulsivity and sensation-seeking) models.

$~$

##### Plot 1

```{r}
check_model(aov(BART ~ barratt_total + sss_total + group, data = tez))
```

$~$

##### Plot 2

```{r}
autoplot(bart_ancova_full, which = 1:6, nrow = 3, ncol = 2)
```

$~$

##### Metrics

```{r}
bart_full_ancova <- aov(BART ~ barratt_total + sss_total + group, data = tez)

bart_full_ancova %>% augment(data = tez) %>%   
  dplyr::select(id, BART, barratt_total, sss_total, 
                .fitted:.std.resid) %>% 
  reactable(compact = T, highlight = T, striped = T,
            columns = list(id = colDef(format = colFormat(digits = 0)),
                           IGT = colDef(format = colFormat(digits = 0)),
                           barratt_total = colDef(format = colFormat(digits = 0)),
                           sss_total = colDef(format = colFormat(digits = 0))), 
            defaultColDef = colDef(
              format = colFormat(separators = T, digits = 3)))
```

$~$

## Building the Model {.tabset .tabset-fade}

$~$

### IGT Model

$~$

First of all, let's see if the groups differ in their IGT scores before including the covariates.

```{r}
igt_anova <- aov(formula = IGT ~ group, data = tez)

summary(igt_anova)

report(igt_anova)
```

$~$

It seems there is no difference on IGT scores between our groups.

We can try to include our covariates into the model and see if we can get groups to significantly differ after controlling for the covariates. 

Since we had specific hypotheses beforehand, we can start by setting up orthogonal contrasts.

We want to do comparisons in this way:

1. Experimental Groups vs Control
2. Punishing vs Non-punishing Groups

```{r}
control_vs_exp <- c(1, 1, -2)
between_exp <- c(1, -1, 0)

contrasts(tez$group) <- cbind(control_vs_exp, between_exp)
```

$~$

#### Step-by-step

We will build up to our full ANCOVA model, meaning we'll create 3 more models:

1. Controlling for impulsivity
2. Controlling for sensation-seeking
3. Controlling for impulsivity + sensation-seeking

$~$

##### 1. Controlling for Impulsivity

```{r}
igt_impuls_ancova <- aov(IGT ~ barratt_total + group, data = tez)

summary.lm(igt_impuls_ancova)
```

$~$

##### 2. Controlling for Sensation-seeking

```{r}
igt_sensSeek_ancova <- aov(IGT ~ sss_total + group, data = tez)

summary.lm(igt_sensSeek_ancova)
```

$~$

##### 3. Controlling for Impulsivity + Sensation-seeking

```{r}
igt_full_ancova <- aov(IGT ~ barratt_total + sss_total + group, data = tez)

Anova(igt_full_ancova, type = "III")

summary.lm(igt_full_ancova)
```

It seems after controlling for impulsivity and sensation-seeking, our groups do not differ significantly.

$~$

##### Comparing Models

```{r}
compare_performance(igt_anova, igt_impuls_ancova, igt_sensSeek_ancova, igt_full_ancova) %>% 
  flextable() %>% colformat_double(digits = 2)
```

```{r}
plot(compare_performance(igt_anova, igt_impuls_ancova, igt_sensSeek_ancova, igt_full_ancova))
```

### BART Model

$~$

Again, let's see if the groups differ in their IGT scores before including the covariates.

```{r}
bart_anova <- aov(BART ~ group, data = tez)

summary.lm(bart_anova)

report(bart_anova)
```

$~$

#### Step-by-step

We will build up to our full ANCOVA model, meaning we'll create 3 more models:

1. Controlling for impulsivity
2. Controlling for sensation-seeking
3. Controlling for impulsivity + sensation-seeking

$~$

##### 1. Controlling for Impulsivity

```{r}
bart_impuls_ancova <- aov(BART ~ barratt_total + group, data = tez)

summary.lm(bart_impuls_ancova)
```

$~$

##### 2. Controlling for Sensation-seeking

```{r}
bart_sensSeek_ancova <- aov(BART ~ sss_total + group, data = tez) 

summary.lm(bart_sensSeek_ancova) 
```

##### 3. Controlling for Impulsivity + Sensation-seeking

```{r}
bart_full_ancova <- aov(BART ~ barratt_total + sss_total + group, data = tez)

summary.lm(bart_full_ancova)
```

It seems none of our models are statistically significant.

$~$

##### Comparing Models

```{r}
compare_performance(bart_anova, bart_impuls_ancova, bart_sensSeek_ancova, bart_full_ancova) %>% flextable() %>% colformat_double(digits = 2)
```

```{r}
plot(compare_performance(bart_anova, bart_impuls_ancova, bart_sensSeek_ancova, bart_full_ancova))
```


```{r}
contrasts(tez$group) <- contr.SAS(3)

summary.lm(aov(IGT ~ intuRelig_total + group, tez))

summary.lm(aov(IGT ~ intuRelig_total, tez))

summary.lm(aov(IGT ~ intuRelig_total + group, tez))

summary(aov(god_exists_rating ~ group, tez))
report(aov(god_exists_rating ~ group, tez))
```










